On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex
12/5 evening..

Assume $w[i]$ forms no bond.
If $S[i] \in \{t_s, t_o\}$, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
Observe that the bead $w[i-1]$ is at the entrance of the previous tunnel or inside.
It is when a bead is stabilized at the entrance of a tunnel that the troll of the tunnel decreases binding capability.
Thus, the inequality does not rely on the troll of previous tunnel.
If $S[i] = t_a$, Lemma~\ref{TTT_tunnelC_lemma} implies $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
That is, this inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed
%According to Lemma~\ref{TTT_tunnelC_lemma}, on Statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
%Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
%If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
%In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
%That is, one subsequence decrease binding capability.

@@

\begin{figure} [tb]
  \begin{center}
  \begin{tabular}{c c c}
 \begin{minipage}{0.3\hsize}
 \centering
    \begin{tikzpicture}
      \draw[white] (0:0)-- (60:2);

>>>>

Assume $w[i]$ forms no bond.
If $S[i] \in \{t_s, t_o\}$, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
Observe that the bead $w[i-1]$ is at the entrance of the previous tunnel or inside.
It is when a bead is stabilized at the entrance of a tunnel that the troll of the tunnel decreases binding capability.
Thus, the inequality does not rely on the troll of previous tunnel.
If $S[i] = t_a$, Lemma~\ref{TTT_tunnelC_lemma} implies $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
%The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
This inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed

@@

\begin{figure} [tb]
  \begin{center}
  \begin{tabular}{c c c}
 \begin{minipage}{0.3\hsize}
 \centering
    \begin{tikzpicture}
      \draw[white] (60:2) circle [radius=0.05];
      \node[above, white] at (60:2) {$n_adj$};
